---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rhdb

<!-- badges: start -->
<!-- badges: end -->

rhdb provides an R interface into the Burea of Reclamation's public facing hydrologic database (HDB). This package queries HDB throght the API at [https://www.usbr.gov/lc/region/g4000/riverops/_HdbWebQuery.html](https://www.usbr.gov/lc/region/g4000/riverops/_HdbWebQuery.html).

## Installation

rhdb is currently only available on GitHub and can beinstalled as follows:

``` r
# install.packages("remotes")
remotes::install_github("BoulderCodeHub/rhdb")
```

## Usage

rhdb can be used to query observed and modeled data from HDB. The data are returned in a data frame. At this time, it is up to the user to know the Site-Datetype ID (sdi) and the server that sdi is stored on. The model run id (mrid) only needs to be specified when querying modeled data.

rhdb includes only one exported function: `hdb_query()`. This can be used to match all queries that are possible from the above link. 

For example, Lake Powell's daily historical elevation and release for January 1-10, 2020 can be queried as follows:

```{r}
library(rhdb)

df <- hdb_query(c(1872, 1928), "uc", "daily", "2020-01-01", "2020-01-10")
df
```

Additionally, Lake Mead's projected elevations from the December 2018 24-Month Study model can be queried:

```{r}
df <- hdb_query(1930, "lc", "monthly", "2018-12", "2019-12", mrid = 3081)
df
```

## Log

* 2020-08-21: version 0.1.0
